```{r setup, cache=FALSE, include=FALSE}
library(knitr)
opts_chunk$set(fig.width=11, fig.height=12, base64_images=F, fig.align="center", message=F, warning=F, fig.path='figure_comparison/')
```

```{r}

library(centWaveP)
library(xcms)
library(gridExtra)
library(ggplot2)

set.seed(21)

eic.l = readRDS("../../../Projects/Shoulder Peaks/eic.l.rds")

```



eics = sample(eic.l, 30)


funcs = list(
  function(x) {baseline::baseline(x, method = "irls")@baseline},
  function(x) {baseline::baseline(x, method = "rfbaseline", span = 1/3)@baseline},
  function(x) {baseline::baseline(x, method = "als")@baseline},
  function(x) {baseline::baseline(x, method = "lowpass")@baseline},
  function(x) {baseline::baseline(x, method = "peakDetection")@baseline},
  function(x) {baseline::baseline(x, method = "modpolyfit")@baseline},
  function(x) {baseline::baseline(x, method = "rollingBall")@baseline}
  )

foo = lapply(seq_along(funcs), function(i) {
f = funcs[[i]]
  foo = lapply(eics, function(eic) {
    eic = as.data.frame(eic)
    
    s = matrix(eic$i, nrow = 1)
    s[s==0] = 1

  eic$b = c(tryCatch(f(s),  error=function(e) { rep(1E9, length(s)) }))
  
  ggplot(eic) + geom_line(aes(x = rt, y = i)) + geom_line(aes(x = rt, y = b, colour = "red")) + theme(legend.position="none", axis.title= element_blank(), axis.text = element_blank()) + ggtitle(i)
    })
  
  do.call(grid.arrange, foo)
})
  

```{r}

eics = sample(eic.l, 30)

funcs = cbind(
  lambda = c(6),
  p = c(0.05, 0.1, 0.025, 0.2)
  )

funcs = cbind(
  lambda = c(4:10),
  p = c(0.1)
  )

# 7, 0.1


foo = lapply(seq_along(funcs[,1]), function(i) {
  f = funcs[i,]
  foo = lapply(eics, function(eic) {
    eic = as.data.frame(eic)
    
    s = matrix(eic$i, nrow = 1)
    s[s==0] = 1

  eic$b = c(baseline::baseline(s, method = "als", p = f["p"], lambda = f["lambda"])@baseline)
  
  ggplot(eic) + geom_line(aes(x = rt, y = i)) + geom_line(aes(x = rt, y = b, colour = "red")) + theme(legend.position="none", axis.title= element_blank(), axis.text = element_blank()) + ggtitle(f)
    })
  
  do.call(grid.arrange, foo)
})


```