```{r setup, cache=FALSE, include=FALSE}
library(knitr)
opts_chunk$set(fig.width=11, fig.height=7, base64_images=F, fig.align="center", message=F, warning=F, fig.path='figure_comparison/')
```

# xcms::findPeaks.centWave vs centWaveP

```{r}

library(centWaveP)
library(xcms)
library(gridExtra)

```

## centWaveP
```{r}

file = "../../../Projects/Datasets/2nm118a_nh2_negative_ecoli_1213/2NM118A_HILICAnnoWgN14_2NM111G_12.mzXML"

xr = xcmsRaw(file, profstep=0)

roi.l = cent.xr(xr, ppm = 2, prefilter = c(4,0), maxskip = 5) # ppm is added to both sides
eic.l = lapply(sample(roi.l, 3000), roiToEic, xr, padding=100)
eic.noise.l = lapply(eic.l, estimateBaselineNoise, peakwidth = c(15, 60), minslope.peak = 20000)

peaks = lapply(seq_along(eic.noise.l), function(i) {
  wave(eic.noise.l[[i]], peakwidth = c(15, 70), valleywidth.min = 15, sensitivity = 1, smooth = T)
})

index = lapply(seq(peaks), function(i) {
  wns = peaks[[i]]$descent.fold.above.descentbaseline
  cbind(roi = rep(i, length(wns)), wsn = wns, num = seq_along(wns))
  }) %>% do.call(what = rbind)

nrow(index)
```

### SN < 1
```{r}
ps0 = lapply(sample(which(index[,"wsn"] < 1), 16, replace = T), function(x) {
  plotWavePeak(unname(index[x, "num"]), eic.noise.l[[index[x,"roi"]]], peaks[[index[x,"roi"]]])
})
do.call(grid.arrange, ps0)  
```
### 1 < SN < 2
```{r}
ps1 = lapply(sample(index[,"wsn"] %>% { which(. > 1  & . < 2) }, 16, replace = T), function(x) {
  plotWavePeak(unname(index[x, "num"]), eic.noise.l[[index[x,"roi"]]], peaks[[index[x,"roi"]]])
})
do.call(grid.arrange, ps1)  
```
### 2 < SN < 3
```{r}
ps2 = lapply(sample(index[,"wsn"] %>% { which(. > 2  & . < 3) }, 16, replace = T), function(x) {
  plotWavePeak(unname(index[x, "num"]), eic.noise.l[[index[x,"roi"]]], peaks[[index[x,"roi"]]])
})
do.call(grid.arrange, ps2)
```
### 3 < SN < 4
```{r}
ps3 = lapply(sample(index[,"wsn"] %>% { which(. > 3  & . < 5) }, 16, replace = T), function(x) {
  plotWavePeak(unname(index[x, "num"]), eic.noise.l[[index[x,"roi"]]], peaks[[index[x,"roi"]]])
})
do.call(grid.arrange, ps3)
```
### 5 < SN 
```{r}
ps4 = lapply(sample(index[,"wsn"] %>% { which(. > 5) }, 16, replace=T), function(x) {
  plotWavePeak(unname(index[x, "num"]), eic.noise.l[[index[x,"roi"]]], peaks[[index[x,"roi"]]])
})
do.call(grid.arrange, ps4)
```

## xcms::findPeaks.centWave
```{r}

ROI.list = xcms:::findmzROI(xr, dev = 2*1E-6, minCentroids = 4, prefilter = c(4,0), noise = 0)

peaks.xcms = findPeaks.centWave(xr, ppm = 2, peakwidth = c(15, 60), snthresh = 0, prefilter = c(4,0), noise = 0, ROI.list = sample(ROI.list, 3000))

nrow(peaks.xcms)

head(peaks.xcms)
```


### 1 < SN < 5
```{r}

 ps4 = lapply(sample(peaks.xcms[,"sn"] %>% { which(. > 1 & . < 5) }, 16, replace=T), function(i) {
   scrange = c(peaks.xcms[i,"rtmin"]-30, peaks.xcms[i,"rtmax"]+30)
   scrange[scrange < 1] = 1; scrange[scrange > max(xr@scantime)] = max(xr@scantime)
    eic = rawEIC(xr, mzrange = c(peaks.xcms[i,"mzmin"], peaks.xcms[i,"mzmax"]), rtrange = scrange)
   
    df = data.frame(eic)
    
    ggplot(df) +
      geom_line(aes(x = scan, y = intensity))
   })
do.call(grid.arrange, ps4)

```
### 5 < SN < 10
```{r}

 ps4 = lapply(sample(peaks.xcms[,"sn"] %>% { which(. > 5 & . < 10) }, 16, replace=T), function(i) {
   scrange = c(peaks.xcms[i,"rtmin"]-30, peaks.xcms[i,"rtmax"]+30)
   scrange[scrange < 1] = 1; scrange[scrange > max(xr@scantime)] = max(xr@scantime)
    eic = rawEIC(xr, mzrange = c(peaks.xcms[i,"mzmin"], peaks.xcms[i,"mzmax"]), rtrange = scrange)
   
    df = data.frame(eic)
    
    ggplot(df) +
      geom_line(aes(x = scan, y = intensity))
   })
do.call(grid.arrange, ps4)

```
### 10 < SN < 100
```{r}

 ps4 = lapply(sample(peaks.xcms[,"sn"] %>% { which(. > 10 & . < 100) }, 16, replace=T), function(i) {
   scrange = c(peaks.xcms[i,"rtmin"]-30, peaks.xcms[i,"rtmax"]+30)
   scrange[scrange < 1] = 1; scrange[scrange > max(xr@scantime)] = max(xr@scantime)
    eic = rawEIC(xr, mzrange = c(peaks.xcms[i,"mzmin"], peaks.xcms[i,"mzmax"]), rtrange = scrange)
   
    df = data.frame(eic)
    
    ggplot(df) +
      geom_line(aes(x = scan, y = intensity))
   })
do.call(grid.arrange, ps4)

```
### SN > 100
```{r}

 ps4 = lapply(sample(peaks.xcms[,"sn"] %>% { which(. > 100) }, 16, replace=T), function(i) {
   scrange = c(peaks.xcms[i,"rtmin"]-30, peaks.xcms[i,"rtmax"]+30)
   scrange[scrange < 1] = 1; scrange[scrange > max(xr@scantime)] = max(xr@scantime)
    eic = rawEIC(xr, mzrange = c(peaks.xcms[i,"mzmin"], peaks.xcms[i,"mzmax"]), rtrange = scrange)
   
    df = data.frame(eic)
    
    ggplot(df) +
      geom_line(aes(x = scan, y = intensity))
   })
do.call(grid.arrange, ps4)

```